---
title: "Python"
author: "Danielle De La Paz"
date: "5/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hey Y'all!
Welcome to my first Python Blog Post!
Before I dive right in, please enjoy this picture of my doggo Tipsy! I got her as a present when I was studying for my DAT and we've been best friends ever since !!!


To start, in my SDS 348 class we have been learning about the interaction between R code and Python. I thought it would be neat to discuss how they interact with each other. To begin I included an R code chunk to show you how the two can work together!!

R code:
```{r} 
install.packages('reticulate',repos = "http://cran.us.r-project.org")
library(reticulate)
Tipsy<- "Tipsy is a Future Dental"
```

Python code:
```{python}
Tipsy="Doggo"
print(r.Tipsy,Tipsy)
```
Hehehe as y'all know I aspire to become a Dentist so I thought it would only be appropriate to include my bestie in the code. This code begins with an R chunk followed by  a python chunk, within the function "print" I was able to access the R defined object to make a complete sentence. 

Another cool feature in Python is finding how many times a certain instance occcurs within a string.
Below are a couple examples of how python can take a long string and find how many times something occurs.

The first thing were going to search for is exactly how many times does the word "dog" occur followed by anything.

```{python}
import re
x="dog doggy dogwalker dogggo odddog funnydog dogsgonewild wholetthedogsout"
re.findall(r"dog.",x) 
```
This shows that there are 8 matches of the word "dog" followed by anything.

The next example were going to search for is exactly how many times the letter d appears followed by anything than the letter g occurs.

```{python}
re.findall(r"d.g",x)
```
This example also shows that there are 8 matches of the letter "d" followed by anything than the letter "g".

Another cool python function is being able to filter a list with the function "regex". In this example I will use a list with multiple strings and use filter to match the pattern I want from the list. This certain list is names I thought about naming tipsy before I got her. The pattern I am looking for is how many names start with the letter "j". 
 

```{python}
import re 
s=["june", "junebug", "july", "bunny", "martini", "jane","joy"]

list(filter(lambda x: re.search(r'^j',x),s))
```

